\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

If there is a vortex with flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix). This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices}.

@@

\SuperScreen requires Python version 3.6 - 3.9. The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository. At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$. Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is hosted by Read the Docs at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}. Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index. The source code and documentation are covered by the MIT License.

@@

param = Parameter(f, a=0, b=1)
print(param) # Parameter<f(a=0, b=1)>

other_param = Parameter(f, a=2, b=3)
print(other_param) # Parameter<f(a=2, b=3)>

print(param(0, 0) == f(0, 0, a=0, b=1)) # True
print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True

param_squared = param ** 2
print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>

print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
) # True
\end{minted}
\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
\label{code:parameters}
\end{code}

@@

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}. The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles). The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization. After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

fig, axes = plt.subplots(2, 2, figsize=(6, 6), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes, (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle size and density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
%   \caption{\inline{optimesh_steps=400}.}
%   \label{fig:circular_ring_mesh}
% \end{subfigure}%
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
%   \caption{\inline{optimesh_steps=None}.}
%   \label{fig:circular_ring_mesh_no_opt}
% \end{subfigure}%
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
%   \caption{\inline{optimesh_steps=400}.}
%   \label{fig:square_ring_mesh}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
%   \caption{\inline{optimesh_steps=None}.}
%   \label{fig:square_ring_mesh_no_opt}
% \end{subfigure}
% \caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
% \label{fig:ring_mesh}
% \end{figure}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Simulate the response to a uniform applied field of 0.25 mT
applied_field = sc.sources.ConstantField(0.25)
field_units = "mT"

solutions = sc.solve(
    device=ring,
    applied_field=applied_field,
    field_units=field_units,
)
assert len(solutions) == 1 # Since there is only one layer
uniform_field = solutions[-1]

# Simulate a current circulating around the hole in the ring.
circulating_currents = {"hole": "1 mA"}

solutions = sc.solve(
    device=ring,
    applied_field=None,
    circulating_currents=circulating_currents
)
assert len(solutions) == 1 # Since there is only one layer
trapped_flux = solutions[-1]

for solution in (uniform_field, trapped_flux):
    solution.plot_currents(
        figsize=(6, 7), cross_section_ys=[0], units="mA/um",
    )
    solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
\end{minted}
\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{ring} device given a uniform applied field, and circulating current with no applied field.}
\label{code:ring_circulating_current}
\end{code}

Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{ring} device. First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field). The resulting sheet current and magnetic field distributions can be visualized using the \inline{plot_current()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:ring_plot_fields_currents}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
    \caption{Caption}
    \label{fig:square-ring-results}
\end{figure}

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
%   \caption{Uniform applied field.}
%   \label{fig:circular_ring_plot_currents}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
%   \caption{Uniform applied field.}
%   \label{fig:circular_ring_plot_fields}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
%   \caption{Trapped flux.}
%   \label{fig:square_ring_plot_currents}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
%   \caption{Trapped flux.}
%   \label{fig:square_ring_plot_fields}
% \end{subfigure}

% \caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
% \label{fig:ring_plot_fields_currents}
% \end{figure}

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).

>>>>

If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix). This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices} as described in Ref.~\cite{brandt_thin_2005}.

@@

\SuperScreen requires Python version 3.6--3.9. The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository. At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$. Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is located at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}. Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index. The source code and documentation are covered by the MIT License.

@@

param = Parameter(f, a=0, b=1)
print(param) # Parameter<f(a=0, b=1)>
other_param = Parameter(f, a=2, b=3)
print(other_param) # Parameter<f(a=2, b=3)>
print(param(0, 0) == f(0, 0, a=0, b=1)) # True
print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
param_squared = param ** 2
print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
) # True
\end{minted}
\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
\label{code:parameters}
\end{code}

@@

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}. The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles). The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate and visualize the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
\label{code:mesh_generation}
\end{code}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but does tend to make the triangle size and density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}

@@

\begin{code}
\begin{minted}[fontsize=\small]{python}
import numpy as np

# Simulate the response of the square ring to a uniform applied field of 0.5 mT
applied_field = sc.sources.ConstantField(0.5)
field_units = "mT"
solutions = sc.solve(
    device=square_ring, applied_field=applied_field, field_units=field_units
)
assert len(solutions) == 1 # Since there is only one layer in this Device
uniform_field_solution = solutions[-1]

# Simulate a current circulating around the hole in the ring
# (with no applied field).
trapped_flux_solution = sc.solve(
    device=square_ring, circulating_currents=dict(hole="1 mA"),
)[-1]

# Specify a sequence of (x, y) coordinates to plot cross-sections
# of the simulated currents and fields.
xs = np.linspace(-5.5, 5.5, 201) # [microns]
cross_sections = [ # Two sets of [x, y] coordinates
    np.stack([xs, xs], axis=1), # diagonal cross-section
    np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
]
for solution in (uniform_field_solution, trapped_flux_solution):
    solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
    solution.plot_fields(cross_section_coords=cross_sections)
\end{minted}
\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
\label{code:ring_circulating_current}
\end{code}

Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{square_ring} device, which was generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}. First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field). The resulting sheet current and magnetic field distributions (calculated using the optimized mesh shown in Figure~\ref{fig:mesh}d) can be visualized using the \inline{plot_currents()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:square-ring-results}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) or trapped flux inducing a circulating current of 1 mA (c, d). The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d), as shown in Code Block~\ref{code:ring_circulating_current}. For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
    \label{fig:square-ring-results}
\end{figure}

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
    }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Figure~\ref{fig:square-ring-results} and Section~\ref{section:overview:visualization}).
